Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-28 paper/paper.tex
minor change

\vspace{1ex}
\noindent\textbf{Overview.}~To create rules, \tname\ leverages (1)
benign and malicious network traffic and (2) rules from public
rulesets. \tname\ takes on input malicious and benign traffic and a
set of rules from public rulesets and produces on output a list of
\emph{plausible rules}---\ie{}, rules that isolate the malicious
traffic from the benign traffic---in order of their likelihood to
reflect user's intent. Figure~\ref{fig:overview} shows the workflow of
\tname{} as a pipeline of three components, which appear numbered in
the figure.  Public data sets of benign
traffic~\cite{tcpreplay,stratosphere-normal} and \nids\ rules
exist~\cite{emerging-threats-open}. Consequently, a user of \tname{}
only needs to provide the malicious traffic on input.

>>>>

\vspace{1ex}
\noindent\textbf{Overview.}~To create rules, \tname\ leverages (1)
benign and malicious network traffic and (2) rules from public
rulesets. \tname\ takes on input malicious and benign traffic and a
set of rules from public rulesets and produces on output a list of
\emph{plausible rules}---\ie{}, rules that isolate the malicious
traffic from the benign traffic---ranked in order of similarity with
existing rules. Figure~\ref{fig:overview} shows the workflow of
\tname{} as a pipeline of three components, which appear numbered in
the figure.  Public data sets of benign
traffic~\cite{tcpreplay,stratosphere-normal} and \nids\ rules
exist~\cite{emerging-threats-open}. Consequently, a user of \tname{}
only needs to provide the malicious traffic on input.
